\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.

%\usepackage[utf8]{inputenc}
%\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage[tight,footnotesize]{subfigure}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[noadjust]{cite} %[5]-[12]
%\usepackage[ruled,vlined]{algorithm2e}
\usepackage{balance}
\usepackage[font=bf]{caption}

%\linespread{0.992}

\begin{document}

\bstctlcite{IEEEexample:BSTcontrol}
\title{Future Generation Multi-tier Video Streaming Networks}

\author{
\IEEEauthorblockN{
Eduardo~S.~Gama\IEEEauthorrefmark{2}, 
Lucas Otavio Nascimento De Araujo\IEEEauthorrefmark{2},
Roger~Immich\IEEEauthorrefmark{4}, and 
Luiz~F.~Bittencourt\IEEEauthorrefmark{2}}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Institute of Computing - State University of Campinas (UNICAMP), Brazil}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Federal University of Rio Grande do Norte (UFRN), Brazil}
eduardogama@lrc.ic.unicamp.br, l240106@dac.unicamp.br, \\ roger@imd.ufrn.br, and bit@ic.unicamp.br}

\maketitle

\begin{abstract}
Video streaming services represent most internet traffic, and according to Cisco forecasts, in 2021, 70\% of all internet traffic will be dominated by video streaming. This includes current video services as well as innovative services such as Real-Time video Streaming and future cloud gaming, whereas, for mobile devices, this estimate represents 78\% of all mobile data traffic. A good cloud architecture partially solves some issues related to the live stream and Video on Demand (VoD) services to accommodate video traffic. However, a centralized cloud service introduces some issues such as higher latency and core network congestion. 
Therefore, to improve video services, it is paramount to distribute video streams according to their requirements properly: a real-time video streaming infrastructure is an interactive service that needs reduced delays (a few milliseconds). At the same time, a non-interactive VoD delivery can tolerate higher delays without impairing the quality of experience. 
This work discusses and gives evidence for the need for proper management and orchestration of video delivery over the Internet as it is core to the smooth coexistence of video services in multi-tier edge/cloud environments. 
The results assessment corroborate that well-defined video management can considerably increase the end-user QoE.


%Video streaming services have been experiencing changes in the recent years, where the number of users consuming a variety of video streaming has been increasing exponentially in Video-on-Demand~(VoD) platforms. In order to accommodate the growing video traffic demand, new solutions have to be designed for the Future of the Internet to provi   de good users' Quality of Experience~(QoE).
%However, a centralized cloud service has some problems, such as increased latency and congestion at the core of the network. Therefore, in order to improve video services, it is of utmost importance to properly distribute video streams according to your requirements: a real-time video infrastructure in a cloud is an interactive service that needs reduced delays (a few milliseconds), while a non-interactive VoD delivery can tolerate longer delays without impairing the quality of the experience. Proper management and orchestration of video delivery over the Internet is essential for the smooth coexistence of heterogeneous video services. This project proposes the use of the fog/cloud hierarchy to design a cooperative video streaming, implementing a set of mechanisms capable of offering an improved Quality of Experience~(QoE) to end users. In this way, this research project proposes to evaluate the impact on the performance of VoD introduced by new distributed computing infrastructures in edge/cloud computing scenarios.
%No entanto, um serviço de nuvem centralizado apresenta alguns problemas, como maior latência e congestionamento da núcleo da rede. Portanto, para melhorar os serviços de vı́deo, é de suma importância distribuir adequadamente os fluxos de vı́deo de acordo com seus requisitos: uma infraestrutura de vı́deos em tempo real em nu- vem é um serviço interativo que precisa de atrasos reduzidos (alguns milissegundos), enquanto uma entrega de VoD não interativa pode tolerar maior atraso sem prejudicar a qualidade da experiência. Um gerenciamento e orquestração adequados da entrega de video pela Internet é essencial para a coexistência suave de serviços de vı́deo heterogêneos. Este projeto propõe o uso da hierarquia de névoa/nuvem para projetar um streaming de video DASH cooperativo em Cidades Inteligentes, implantando um conjunto de mecanismos capaz de oferecer uma Qualidade de Experiência (QoE) aprimorada para usuários finais.
\end{abstract}

\begin{IEEEkeywords}
Edge computing, Cloud computing, Quality of Experience, Video Streaming, Video-on-Demand, VoD
\end{IEEEkeywords}


\input{introduction}

\input{related-work}

\input{system-archi}

\input{results}

\input{conclusion}

\section*{Acknowledgment}
This research is part of the INCT of the Future Internet for Smart Cities funded by CNPq proc. 465446/2014-0, Coordenação de Aperfeiçoamento de Pessoal de Nível Superior – Brasil (CAPES) – Finance Code 001, FAPESP procs. 14/50937-1, 15/24485-9, and 2020/16763-7.

\begin{small}
    \bibliographystyle{unsrt}
    \bibliography{references}
\end{small}

%\vspace{12pt}

\end{document}
